Analysis 3

### 2023-11-29 Lahman Analysis/Rough Analysis 2/Analysis3.qmd
Work from Thanksgiving Break
Made model 3aa work
Noticed that model 3aa wasn't on the "Analysis3.qmd" file for my, but was able to parse through the Git history (thanks Dr.Parson) and figure out how we made it work and then put it onto the document.

@@

```{r}
data3b <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2,
  cAgeCb = (Samp_Batting %>% pull(Age) -30)**3,
  cAgeQa = (Samp_Batting %>% pull(Age) -30)**4,
  Park = Samp_Batting %>% pull(park_index)
)
```

```{r}
fit3b <- stan(
  file = "HR3b.stan",
  data = data3b,
  iter = 200
)
```

>>>>

While these previous thoughts and conerns are fair, in my ultimate model I hope to use about 1000 players or so. Then, it will be much less likely that all years aren't considered. We could also just manipulate the seed such that we make sure that all years are covered from 1973-2019. This may violate the randomness of the sample though. There is at least an argument to be made.

Moreover, I want to make this model including the year factor so I have something to reference back to if I want to include the year in the ultimate model.

```{r}
data3aaa <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  n_park = n_distinct(Samp_Batting$park_index),
  n_year = n_distinct(Samp_Batting$yearID),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2,
  Park = Samp_Batting %>% pull(park_index),
  Year = Samp_Batting %>% pull(yearID) -1972
)
```

```{r}
fit3aaa <- stan(
  file = "HR3aaa.stan",
  data = data3aaa,
  iter = 200
)
```

This probably wouldn't even run, so why waste time on it. I would probably end up having the problem I had with the stadiums a couple weeks ago where (since the reference indexes weren't consecutive) Stan threw a fit and wouldn't let anything run.

@@

```{r}
data3aa <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  n_park = n_distinct(Samp_Batting$park_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2,
  cAgeCb = (Samp_Batting %>% pull(Age) -30)**3,
  cAgeQa = (Samp_Batting %>% pull(Age) -30)**4,
  Park = Samp_Batting %>% pull(park_index)
)
```

```{r}
fit3b <- stan(
  file = "HR3aa.stan",
  data = data3aa,
  iter = 200
)
```
